\vspace{.5cm} \textcolor{white} {Spin Canonical Rings of Log Stacky Curves}

### 2015-09-25 poster-curves/spin-canonical-poster-v2.tex
edited saint-donat
posters: turn draft mode off
edited last poster example, corrected some more typos

\documentclass[a0,landscape, draft]{a0poster}
\usepackage{etex}

@@

\noindent
with multiplication structure corresponding to tensor product of
sections. In the case that $g \geq 2$, $\Omega_X$ is ample and
therefore $X \cong \proj R$. When $g \geq 2$, Petri's theorem 
shows that, in most cases, $R(X, K_X)$
is generated in degree 1 with relations in degree 2 (see
Saint-Donat \cite[p. 157]{saint-donat:proj}. This has the pleasant 
geometric consequence that canonically embedded curves of genus $\geq 4$ which are not hyperelliptic curves, trigonal curves, or plane quintics are scheme-theoretically cut out by degree 2 equations.

@@

\begin{center}
\begin{tabular}
{| c || c | c | c |}
	\hline
	$\halfcan'$ & Generator Degrees & Degrees of Minimal Relations & $e$ \\
	\hline
	\hline
	$P - Q$ & $\{2\}$ & $\emptyset$ & $1$\\	\hline

@@

\begin{corollary}
\label{corollary:main-mod-forms}
Let $\Gamma$ be a Fuchsian group, i.e., $\Gamma \backslash \BH$ has finite area,and let $\sx$ be a stacky curve
associated to $\Gamma \backslash \BH$ with signature $\sigma
= (g; e_1, \ldots, e_r; \delta)$.

Except in an explicit finite list of cases, the
ring of modular forms $M(\Gamma)$ is generated as a $k$-algebra
by elements of degree at most $\max(5, e_1, \ldots, e_r)$ with
relations generated in degree at most $2 \cdot \max(5, e_1, \ldots, 
e_r)$.
\end{corollary}

@@

>>>>

\documentclass[a0,landscape]{a0poster}
\usepackage{etex}

@@

\noindent
with multiplication corresponding to tensor product of
sections. In the case that $g \geq 2$, $\Omega_X$ is ample and
therefore $X \cong \proj R$. When $g \geq 2$, Petri's theorem 
shows that, in most cases, $R(X, K_X)$
is generated in degree 1 with relations in degree 2 \cite[p. 157]{saint-donat:proj}. This has the pleasant 
geometric consequence that canonically embedded curves of genus $\geq 4$ which are not hyperelliptic curves, trigonal curves, or plane quintics are scheme-theoretically cut out by degree 2 equations.

@@

\begin{center}
\begin{tabular}
{| c || c | c | c |}
	\hline
	$\halfcan$ & Generator Degrees & Degrees of Minimal Relations & $e$ \\
	\hline
	\hline
	$P - Q$ & $\{2\}$ & $\emptyset$ & $1$\\	\hline

@@

\begin{corollary}
\label{corollary:main-mod-forms}
Let $\Gamma$ be a Fuchsian group, i.e., $\Gamma \backslash \BH$ has finite
area, and let $\sx$ be a stacky curve
associated to $\Gamma \backslash \BH$ with signature $\sigma
= (g; e_1, \ldots, e_r; \delta)$.

Except in an explicit finite list of cases, the
ring of modular forms $M(\Gamma)$ is generated as a $\Bbbk$-algebra
by elements of degree at most $\max(5, e_1, \ldots, e_r)$ with
relations generated in degree at most $2 \cdot \max(5, e_1, \ldots, 
e_r)$.
\end{corollary}

@@

\begin{example}  
	\hspace{1mm}
	\begin{center}
    $D = K + \Delta = \frac{1}{2}P + \frac{2}{3}Q -\infty$
  \end{center}

\begin{center}
\begin{tabular}{ |c| c| c| c|c|}
\hline
$d$ & $\lfloor dD \rfloor$ & $\deg \lfloor dD \rfloor$ &  $\dim H^0(X,\lfloor dD \rfloor)$  & $M_{2d}(SL_2(\BZ))$  \\ 
\hline
0& 0& 0&  1& 1 \\ 
1&$-\infty$&-1& 0&  0 \\  
2&$P + Q -2\infty$&0& 1&  $E_4$  \\
3&$P + 2Q -3\infty$&0& 1&  $E_6$  \\
4&$2P + 2Q -4\infty$&0& 1&  $E_4^2$  \\
5&$2P + 3Q -5\infty$&0& 1&  $E_4E_6$  \\
6&$3P + 4Q -6\infty$&1& 2& $E_4^3, E_6^2$   \\
\hline
\end{tabular}
\end{center}
\end{example}
